Draft information

### 2019-05-13 paper/draft-info.Rmd
Update draft info

---
title: "Draft information"
subtitle: "version: draft-4.0"
date: "2019-04-26"
# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

@@

* Specify grant numbers in the Awknoledgements and make sure the ones stated there now are correct. 
* Aprove (or not for submission)

## Changes since last draft

* Added .git and .drake to .dockerignore to speed up build
* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
* Many minor changes to the text
* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology). 
* Some extra refs added
* Moved the sentences about variable collinearity to the supp. info. to save a bit of space in the main text
* Removed criteria #2...

>>>>

---
title: "Draft information"
subtitle: "version: draft-6.0"
date: "2019-05-XX"
# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

@@

* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
* Suggestions to bring the abstract down to 150 words.
* Approve (or not) for submission.

## Changes since the last draft

* Fixed typos and minor wording mistakes
